---
title: "Cambridge Bioinformatics Hackathon - Will"
output: html_notebook
---

Load the required libraries

```{r}
library(tidyverse)
library(skimr)
library(DataExplorer)
```

Load the data

```{r}
data <- read.delim("C:/Users/willy/OneDrive/Desktop/Existing_Course_Data/Existing_Course_Data/R_Stats_Course_Data/exam.anxiety.dat")
data
```
Explore the dataset

```{r}
dim(data)
glimpse(data)
```


```{r}
summary(data)
```


```{r}
skim(data)
```

Create a report with the Data Explorer - this will output a file with a brief summary of the dataset.

```{r}
#DataExplorer::create_report(data)
```

# Distribution of Gender

```{r}
library(forcats)
ggplot(mutate(data, Gender = fct_infreq(Gender))) + geom_bar(aes(x = Gender, fill = Gender)) + ggtitle("Distribution of Gender")
```


# Distribution of Exam results

```{r}
data %>%
ggplot(aes(Exam, color = Gender, fill = Gender)) + 
  geom_histogram() + 
  facet_wrap(~Gender) + ggtitle("Distribution of Exam Results")
```

# Distribution of Anxiety scores

```{r}
data %>%
ggplot(aes(Anxiety, color = Gender, fill = Gender)) + 
  geom_histogram() + 
  facet_wrap(~Gender) + ggtitle("Distribution of Anxiety Scores")
```

# Scatterplot to demonstrate the relationship between anxiety and revision.

```{r}
data %>%
ggplot(aes(Anxiety, Revise, color = Gender)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) + 
  facet_wrap(~Gender) + ggtitle("Assessing the relationship between Anxiety and Revision")
```

# Obtain corrplot for the dataset

```{r}
#install.packages("corrplot")
library(corrplot)
```

```{r}
num_cols <- unlist(lapply(data, is.numeric))         # Identify numeric columns
num_cols
```


```{r}
num_data<-data[ , num_cols] 
corrdata<-cor(num_data)
head(round(corrdata,2))
corrplot(corrdata, method = "number") 
```
This correlation plot indicates that there is:
1) A strong negative relationship between anxiety and revision. This is to be expected as increased revision leads to a decrease in anxiety
2) A moderate positive correlation between exam and revision but a moderate negative correlation between exam and anxiety.

